---
title: "2019, chirunconf: Application"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  eval = FALSE,
  comment = "#>"
)
```

* [Application form](https://docs.google.com/forms/d/1Vc8jHxXlZ_ZDzRNFX5eX58avS66fA_ayX1p3FyfO_e4/viewform?edit_requested=true)

* [Information](https://chirunconf.github.io)

Next are the questions and answers that I believe are most useful to share.

### Social media

> Please provide any relevant social media account information that you would like to help us gauge your involvement in the R community. Additionally, we may ask you to use these accounts on our website if you are selected to attend.

Twitter Handle: \@mauro_lepore (<https://twitter.com/mauro_lepore>)

GitHub Username: maurolepore (<https://github.com/maurolepore>)

Blog URL: <http://bit.ly/mauro-lepore-blog-fgeo>

LinkedIn URL: <http://bit.ly/mauro-lepore-linkedin>

Any other links: <http://bit.ly/mauro-lepore-about>

### Background

#### Briefly describe any personal or community-related R accomplishment that you are most proud of. If possible, please include any relevant links. *

What I am most proud of is that in the last couple of years I have participated in multiple and diverse communities that support open software, reproducible research, and diversity, including rOpensci, The Carpentries, LatinR, and R-Ladies (<http://bit.ly/mauro-lepore-about>). 

### Interests

#### Why do you want to attend this unconf? *

> Describe what you see as your long-term goals, and how will attending this unconf help you reach them.

My long term goal is to help to improve some aspect of our social and natural environment, by working in data science with people whose work and behavior I admire. Attending this unconf will help me to reach this goal by connecting me with like-minded people, who I can support and learn from. Those selected to attend this unconf will likely be the kind of people I would love to work with. 

#### What do you specifically hope to learn or accomplish at this unconf (e.g. develop a package, submit your first pull request)? *

I hope to learn alternative ways of solving data science problems. My own ideas can never be as many or good as those developed by a team of people with diverse opinions and experiences.

Although I'm very open to work on exciting projects proposed by someone else, here are two specific projects I propose:

(1) datos: A package containing datasets for the translation to Spanish of the book R for Data Science (<https://github.com/cienciadedatos/datos>).

(2) pkgdoc: A package to centralize, search, and link documentation of multiple R packages (<https://maurolepore.github.io/pkgdoc/>). pkgdoc may be used to present and link the R packages developed during Chicago R Unconference (demo: <http://bit.ly/pkgdoc-demo-chirunconf>).

For both of these projects the goal would be to get this package closer to submission to CRAN or rOpenSci.

#### Briefly describe what would make a successful unconf for you. For example, are there specific new skills you are hoping to learn, projects you want to work on, or contacts you are looking to make?

To me, a successful unconf would look like this:

* I learn something new that can improve my work.
* I teach something new to someone that can improve their work.
* I contribute to a meaningful project (not limited to the projects listed above).
* I connect with new people and strengthen the link with those who I met before.


```{r hide, eval=FALSE, echo=FALSE}
#### How can you help us magnify the impact of this unconf by sharing what you learned? 

I could connect you with Kristen Bullard, the Science Researcher Services Librarian ( <https://library.si.edu/research>). She organizes series of seminars and she may want to invite you to talk about the unconf and spread the idea. These seminars are promoted throughout the Smithsonian. You could deliver the talk from a remote location. Kristen would advertise the talk, provide the video-conference platform, and moderate the meeting. I believe that other community-driven initiatives such as rOpenSci and RLadies-DC have already organized similar talks.

I could also introduce you to Rebecca Dirkow, the leader of the Smithsonian Institution Data Science Lab (<https://datascience.si.edu/people/dr-rebecca-dikow>). Rebecca's team runs Data Carpentry workshops, and I hope you will inspire them to run a Smithsonian runconference.

Also I will be pleased to share my experience with the researchers I work for, an international network of 65+ research groups (ForestGEO <https://forestgeo.si.edu/>). Our regular annual meeting -- this time in China -- is always an excellent opportunity to spread what I learn.
```

#### If you have a blog, frequently attend or speak at meet-ups, have interest or experience teaching others, etc. please share that information here.

<http://bit.ly/mauro-lepore-about>

